### 2016-08-28 paper.tex
Add RVAT parameters to turbine geometry table

\begin{table}[ht]
\centering
\begin{tabular}{l|l|l}
   & Full-scale & Model (1:6) \\
\hline
Diameter (m)   & 6.450 & 1.075 \\
Height (m)     & 4.840 & 0.8067 \\
Blade root chord (m) & 0.4000 & 0.06667 \\
Blade tip chord (m)  & 0.2400 & 0.04000 \\
Blade profile & NACA 0021 & NACA 0021 \\
Blade mount & 1/2 chord & 1/2 chord \\
Blade pitch (deg.) & 0.0 & 0.0 \\
Strut profile & NACA 0021 & NACA 0021 \\
Strut chord (m) & 0.3600 & 0.06000 \\
Shaft diameter (m) & 0.2540 \cite{Beam2011} or 0.4160 \cite{Hill2014} & 0.06350\\
\end{tabular}
\caption{\textbf{RM2 turbine geometric parameters.}}
\label{tab:turb-geom}
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{l|l|l|l}
   & Full-scale RM2 & 1:6 scale RM2 & UNH-RVAT \\
\hline
Diameter (m)   & 6.450 & 1.075 & 1.0 \\
Height (m)     & 4.840 & 0.8067 & 1.0 \\
Blade root chord (m) & 0.4000 & 0.06667 & 0.14 \\
Blade tip chord (m)  & 0.2400 & 0.04000 & 0.14 \\
Blade profile & NACA 0021 & NACA 0021 & NACA 0020 \\
Blade mount & 1/2 chord & 1/2 chord & 1/2 chord \\
Blade pitch (deg.) & 0.0 & 0.0 & 0.0 \\
Strut profile & NACA 0021 & NACA 0021 & NACA 0020 \\
Strut chord (m) & 0.3600 & 0.06000 & 0.14 \\
Shaft diameter (m) & 0.2540 \cite{Beam2011} or 0.4160 \cite{Hill2014} & 0.06350 & 0.095 \\
\end{tabular}
\caption{\textbf{Turbine geometric parameters for both the full-scale and 1:6
scale model RM2 (tested here), along with the UNH-RVAT for comparison.}}
\label{tab:turb-geom}
\end{table}
